\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amssymb}
\usepackage{amsfonts}

\begin{document}

\title{Types Of Learning}
\author{Kelvin $\cdot$ Liang \, ziyoustep@gmail.com}
\date{June, 11, 2018}
\maketitle

\section{Introduction}
In this note, we are going to categorize types of learning by output space, data label, protocol and input space.
\section{Learning with different output space $Y$}
\subsection{Binary Classification}
Answering yes/no questions. $y=\{+1, -1\}$\\
Example: Credit card approval
\subsection{Multiclass Classification}
The classes of the output is more than two. $y=\{1, 2, \cdots , K\}$\\
Example: Written digits pictures $\Rightarrow 1, 2, \cdots , 9$ 
\subsection{Regression}
The output space is $\mathbb{R}$. $y\in \mathbb{R}$\\
Example: Company data $\Rightarrow$ Stock price
\subsection{Structured Learning}
The output is some kind of structure without explicit class definition. In sentence recoginition, the output structure may be like $y=\{PVN, PVP,NVN,\cdots\}$, where $P$ is pronoun, $V$ is verb and $N$ is noun.

\section{Learning with different data label $y_i$}
\subsection{Supervised Learning}
Label all $y_i$ for $i\in \{1,\cdots,n\}$\\
Example: Classify US dollars.
\subsection{Unsupervised Learning}
Label no $y_i$\\
Example: Clustering points on a plane
\subsection{Semi-supervised Learning}
Label some $y_i$\\
This learning method is usually used when labeling is an expensive  operation.
\subsection{Reinforcement Learning}
In reinforcement learning, we do not label $y_i$ explicitly, but implicit it by the feedback $\hat{y_i}$.\\
Example: A dog learn to sit down.

\section{Learning with different protocol $f \to (x_i, y_i)$}
\subsection{Batch Learning}
Input all known data at one time.\\
Example: It's a common protocol. No need to give an example.
\subsection{Online Learning}
Sequentially learning from incoming data.(passive)\\
Example: Gmail classy incoming email as important, spam, promotion etc.
\subsection{Active Learning}
The machine strategically query $y_i$ of chosen $x_i$.

\section{Learning with different input space $X$}
\subsection{Concrete Features}
Give clear physical meaning. The features are determined by human. So, it often include human intelligence on the learning task.
\subsection{Raw Features}
Give simple physical meaning. Often need feature extraction/conversion.
\subsection{Abstract Features}
Give no physical meaning.Need feature extraction/conversion as well.

\section{References}
Almost all of the materials of this note are from Professor Hsuan-Tien Lin , NTU. If you wan to know more information about Machine Learning Foundation, please refer to Professor Lin's homesite.

\end{document}